Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
sec 3.3.

There are two different problems that arise from FWL semantics.  The first
is the error in the dynamics caused by the inability to represent the exact
state of the physical system, while the second relates to rounding errors
during computation.  In~\cite{fialho1994stability}, a stability measure
based on the error of the digital dynamics ensures that the deviation
introduced by FWL does not make the digital system unstable.  A~more recent
approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$ calculus to
directly model the digital controller so that the selected parameters are
stable by design.  The analyses in~\cite{DBLP:conf/hybrid/RouxJG15,
DBLP:conf/hybrid/WangGRJF16} rely on an invariant computation on the
discrete system dynamics using Semi-Definite Programming (SDP).  While the
former uses BIBO properties to determine stability, the latter uses
Lyapunov-based quadratic invariants.  In both cases, the SDP solver uses
floating-point arithmetic and soundness is checked by bounding the error. 
An alternative approach is taken by~\cite{park2016scalable}, where the
verification of given control code is performed against a known model by
extracting an LTI model of the code through symbolic execution.  In order to
account for rounding errors, an upper bound is introduced in the
verification phase.  The work in \cite{picasso2003stabilization,
picasso2002construction} introduces attractive invariant sets as a mechanism
to bound the quantization error effect on stabilisation as an invariant set
that always converges toward the controllable set.  In a similar fashion,
\cite{liberzon2003hybrid} evaluates the dynamics of the quantization error
and bounds its trajectory to a known region over a finite period of time. 
This technique works for both linear and non-linear systems.

@@

Asymptotic stability boils down to Lyapunov stability and convergence to an
equilibrium point~\cite{Astrom08}.  Lyapunov stability requires that model
trajectories remain in a neighborhood of the equilibrium point.  In the case
of closed-loop LTI models as in~\eqref{eq:closedloopss}, the equilibrium
point is the origin (if the reference is equal to zero), or an offset
thereof.  Here, we consider systems with a zero reference signal.

A discrete-time system as \eqref{eq:closedloopss} is asymptotically stable
\textit{iff} all the roots of the characteristic polynomial (i.e., the
eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity
circle in the complex plane, i.e., \textit{iff} their absolute values are
less than one~\cite{astrom1997computer}.  In this paper, we express the
stability specification $\phi_{stability}$ in terms of a check known as
Jury's criterion~\cite{fadali}: this is an easy algebraic formula to select
the entries of matrix $K$, so that the closed-loop dynamics are shaped as
desired.  A detailed description of this specification can be found in
Appendix~\ref{sec:appendix-stability}.

>>>>

There are two different problems that arise from FWL semantics.  The first
is the error in the dynamics caused by the inability to represent the exact
state of the physical system, while the second relates to rounding errors
during computation.  In~\cite{fialho1994stability}, a stability measure
based on the error of the digital dynamics ensures that the deviation
introduced by FWL does not make the digital system unstable.  A~more recent
approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$ calculus to
directly model the digital controller so that the selected parameters are
stable by design.  The analyses in~\cite{DBLP:conf/hybrid/RouxJG15,
DBLP:conf/hybrid/WangGRJF16} rely on an invariant computation on the
discrete system dynamics using Semi-Definite Programming (SDP).  While the
former uses BIBO properties to determine stability, the latter uses
Lyapunov-based quadratic invariants.  In both cases, the SDP solver uses
floating-point arithmetic and soundness is checked by bounding the error. 
An alternative approach is taken by~\cite{park2016scalable}, where the
verification of given control code is performed against a known model by
extracting an LTI model of the code through symbolic execution.  In order to
account for rounding errors, an upper bound is introduced in the
verification phase.  The work in \cite{picasso2003stabilization,
picasso2002construction} introduces attractive invariant sets as a mechanism
to bound the quantization error effect on stabilization as an invariant set
that always converges toward the controllable set.  In a similar fashion,
\cite{liberzon2003hybrid} evaluates the dynamics of the quantization error
and bounds its trajectory to a known region over a finite period of time. 
This technique works for both linear and non-linear systems.

@@

Asymptotic stability implies convergence to an equilibrium point from any states in its neighborhood. This stability concept is stronger than the Lyapunov and BIBO stability researched by previous works~\cite{DBLP:conf/emsoft/RavanbakhshS16,DBLP:journals/corr/AbateBCCDKK16,DBLP:conf/hybrid/RouxJG15,
DBLP:conf/hybrid/WangGRJF16}. In the case of linear systems as 
in~\eqref{eq:closedloopss}, the equilibrium point for zero-input 
response is always the  origin.  Here, we consider systems with 
a zero reference signal.

A discrete-time LTI system as \eqref{eq:closedloopss} is asymptotically stable
\textit{iff} all the roots of the characteristic polynomial (i.e., the
eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity
circle in the complex plane, i.e., \textit{iff} their absolute values are
less than one~\cite{astrom1997computer}.  In this paper, we express the
stability specification $\phi_{stability}$ in terms of a check known as
Jury's criterion~\cite{fadali}: this is an easy algebraic formula to select
the entries of matrix $K$, so that the closed-loop dynamics are shaped as
desired.  A detailed description of this specification can be found in
Appendix~\ref{sec:appendix-stability}.
